---
title: "HW11_Sabrina Liu"
output: html_document
---

#1(a)
#According to graph,the estimated model equation is ln(Ï€/(1 âˆ’ Ï€) = âˆ’7.0 + 0.1A + 1.2S + 0.3R + 0.2R Ã— S.

#1)The estimated odds ratio for having cancer comparing R = 1 versus R = 0 given S = 0: Odds Ë† (R = 1|S = 0) / Odds Ë† (R = 0|S = 0) = exp(âˆ’7.0 + 0.1A + 0.3) / exp(âˆ’7.0 + 0.1A) = exp(0.3) = exp(Î²Ë†R) = 1.35

#We can conclude that for nonsmokers, the odds for squamous cell esophageal cancer are 35% higher for black than for white people.

#2)The estimated odds ratio for having cancer comparing R = 1 versus R = 0 given S = 1: Odds Ë† (R = 1|S = 1) / Odds Ë† (R = 0|S = 1) = exp(âˆ’7.0 + 0.1A + 0.3 + 1.2 + 0.2)/ exp(âˆ’7.0 + 0.1A + 1.2) = exp(0.3+0.2) = exp(Î²Ë†R+Î²Ë†RÃ—S) = 1.65

#We can conclude that for smokers, the odds for squamous cell esophageal cancer are 65% higher for black than for white people.

#3)The estimated odds ratio for having cancer comparing S = 1 versus S = 0 given R = 0: Odds Ë† (S = 1|R = 0) / Odds Ë† (S = 0|R = 0) = exp(âˆ’7.0 + 0.1A + 1.2) / exp(âˆ’7.0 + 0.1A) = exp(1.2) = exp(Î²Ë†S) = 3.32

#We can conclude that for white people, the odds for squamous cell esophageal cancer are 232% higher for smokers than for nonsmokers.

#4)The estimated odds ratio for having cancer comparing S = 1 versus S = 0 given R = 1: Odds Ë† (S = 1|R = 1) / Odds Ë† (S = 0|R = 1) = exp(âˆ’7.0 + 0.1A + 1.2 + 0.3 + 0.2) / exp(âˆ’7.0 + 0.1A + 0.3) = exp(1.2+0.2) = exp(Î²Ë†S+Î²Ë†RÃ—S) = 4.01

#We can conclude that for black people, the odds for squamous cell esophageal cancer are 301% higher for smoker than for non-smokers.

#1(b)
#According to part(a), we can see that e^Î²Ë†R = e^0.30 = 1.65. There is65% increase in the odds for the cancer for black over white people, if S = 0 (for nonsmokers); e^Î²Ë†S = e^1.20 = 3.32, 232% increase in the odds for the cancer for smokers over nonsmokers,if R = 0 (for white people). 

#1(c)
#The estimated model equation is ln(Ï€/(1 âˆ’ Ï€) = âˆ’7.0 + 0.1A + 1.2S + 0.3R + 0.2R Ã— S + 0.4A x R. 

#2(a)
```{r}
D <- c(45,15,40,83,90,25,35,65,95,35,75,45,50,75,30,25,20,60,70,30,60,61,65,15,20,45,15,25,15,30,40,15,135,20,40)
T <- c(0,0,0,1,1,1,0,0,0,0,0,1,1,1,0,0,1,1,1,0,0,0,0,1,1,0,1,0,1,0,0,1,1,1,1)
Y <- c(0,0,1,1,1,1,1,1,1,1,1,1,0,1,0,1,0,1,1,1,1,0,1,0,0,1,0,1,0,1,1,0,1,0,0)
df <- data.frame(D,T,Y)
df
mod.fit <- glm(Y~D+T, data=df, family=binomial)
summary(mod.fit)
```
#2(b)
#According to the summary, we get that when H0: beta1(D) = 0, the p-value is 0.00931, which D is important predictor of probabilty of the odds of being a patient with general anesthesia experienced a sore throat on waking. Patients who use a laryngeal mask airway are more likely to experience a sore throat.

#2(c)
```{r}
mod.fit2 <- glm(Y~D+T+D:T, data=df, family=binomial)
summary(mod.fit2)
exp(0.10308)
```
#1)For tracheal tube T=1: logit(P-hat(Y=1))=-4.42245+0.10308(D)
#2)For laryngeal mask airway T=0: logit(P-hat(Y=1))=0.04979+0.02848(D)
#Therefore,  we can say for a one-unit increase in duration of the surgery, we expect to see about 11% (exp(0.10308)=1.10858) increase in the odds of being a patient with general anesthesia experienced a sore throat on waking, given T=1.

#2(d)
```{r}
anova(mod.fit, mod.fit2, test="Chisq")
```

#P-value = 0.1777 > 0.05 which means the data do not indicate a need for an interaction term in this case. 

#2.4.12(a)
```{r}
library(plyr)
CT2 <- read.table(file = "aptima_combo.csv", header = TRUE, sep = ",")
CT2

CT2$Disease  <- as.factor(CT2$Disease)
mod.fit<-glm(formula = Disease ~ Gender + Specimen + Symptoms_Status, family = binomial(link = logit), data = CT2)
mod.fit 

CT2$gender.numb <- ifelse(test = CT2$Gender == "Female", yes = 0, no = 1)
CT2$sensitivity <- CT2$True_positive/CT2$Sample_size
plot(x = CT2$gender.numb, y = CT2$sensitivity, xlab =
"Gender", ylab = "Sensitivity", type = "n", xaxt = "n") 
axis(side = 1, at = c(0,1), labels = c("Female", "Male")) 
Swab.Symptomatic <- CT2$Disease == "Chlamydia" &
CT2$Symptoms_Status == "Symptomatic" 
lines(x = CT2$gender.numb[Swab.Symptomatic],
CT2$sensitivity[Swab.Symptomatic], type = "o", lty =
"solid", col = "black")
```

#2.4.12(b)
```{r}
CT2$gender.numb <- ifelse(test = CT2$Gender == "Female", yes = 0, no = 1)
CT2$sensitivity <- CT2$True_positive/CT2$Sample_size
plot(x = CT2$gender.numb, y = CT2$sensitivity, xlab =
"Gender", ylab = "Sensitivity", type = "n", xaxt = "n") 
axis(side = 1, at = c(0,1), labels = c("Female", "Male")) 
Swab.Symptomatic <- CT2$Disease == "Gonorrhea" &
CT2$Symptoms_Status == "Symptomatic" 
lines(x = CT2$gender.numb[Swab.Symptomatic],
CT2$sensitivity[Swab.Symptomatic], type = "o", lty =
"solid", col = "black")
```
#We can realaze the level of sensetivity was more affected by Gonorrhea. The gender difference was also more affected by Gonorrhea. 

#2.4.20(a)
```{r}
placekick<-read.table(file = "Placekick.csv", header = TRUE, sep = ",")
head(placekick)
tail(placekick)
mod.fit.Ho<-glm(formula = good ~ distance + wind, family = binomial(link = logit), data = placekick)
  mod.fit.Ha<-glm(formula = good ~ distance + wind + distance:wind, family = binomial(link = logit), data = placekick)
  summary(mod.fit.Ha)
  anova(mod.fit.Ho, mod.fit.Ha, test = "Chisq")
  library(package = car)  # Would need this if it has not already been used.
  Anova(mod.fit.Ha, test = "LR")  # Simpler way for the test
  Anova(mod.fit.Ho, test = "LR")
library(package = multcomp)
K <- matrix(data = c(0, 0, 1, 1*20), nrow = 1, ncol = 4,byrow = TRUE)
linear.combo <- glht(model = mod.fit.Ha, linfct = K) 
ci.log.OR <- confint(object = linear.combo, calpha = qnorm(0.975))
data.frame(estimate = exp(-ci.log.OR$confint[1]), lower = exp(-ci.log.OR$confint[3]), upper = exp(-ci.log.OR$confint[2]))
```

#2.4.20(b)
#Multiple comparisons use the glht function in the multcomp package, so that c(0,0,0,20) can be compared with the amount of 0 and 20.The usage is glht(model = mod.fit.Ha, linfct = K) to get a glht model. If you use summary(glht), you can get a pairwise p value consistent with mod.fit.HA (parameter linfct is linear Hypothetical specification, mcp is a function of multiple comparisons, returning a control group)

#2.4.20(c)
```{r}
#for 30
K <- matrix(data = c(0, 0, 1, 1*30), nrow = 1, ncol = 4,byrow = TRUE)
linear.combo <- glht(model = mod.fit.Ha, linfct = K) 
ci.log.OR <- confint(object = linear.combo, calpha = qnorm(0.975))
data.frame(estimate = exp(-ci.log.OR$confint[1]), lower = exp(-ci.log.OR$confint[3]), upper = exp(-ci.log.OR$confint[2]))

#for 40
K <- matrix(data = c(0, 0, 1, 1*40), nrow = 1, ncol = 4,byrow = TRUE)
linear.combo <- glht(model = mod.fit.Ha, linfct = K) 
ci.log.OR <- confint(object = linear.combo, calpha = qnorm(0.975))
data.frame(estimate = exp(-ci.log.OR$confint[1]), lower = exp(-ci.log.OR$confint[3]), upper = exp(-ci.log.OR$confint[2]))

#for 50
K <- matrix(data = c(0, 0, 1, 1*50), nrow = 1, ncol = 4,byrow = TRUE)
linear.combo <- glht(model = mod.fit.Ha, linfct = K) 
ci.log.OR <- confint(object = linear.combo, calpha = qnorm(0.975))
data.frame(estimate = exp(-ci.log.OR$confint[1]), lower = exp(-ci.log.OR$confint[3]), upper = exp(-ci.log.OR$confint[2]))

#for 60
K <- matrix(data = c(0, 0, 1, 1*60), nrow = 1, ncol = 4,byrow = TRUE)
linear.combo <- glht(model = mod.fit.Ha, linfct = K) 
ci.log.OR <- confint(object = linear.combo, calpha = qnorm(0.975))
data.frame(estimate = exp(-ci.log.OR$confint[1]), lower = exp(-ci.log.OR$confint[3]), upper = exp(-ci.log.OR$confint[2]))
```

#2.4.20(d)
```{r}
K <- matrix(data = c(1, 0, 0, 0, 0, 1, 0, 0, 0, 0, 1, 0, 0, 0, 0, 1), nrow = 4, ncol = 4, byrow = TRUE)
linear.combo <- glht(model = mod.fit.Ha, linfct = K) 
summary(object = linear.combo, test = adjusted(type = "none"))
```

#2.4.20(e)
```{r}
confint(object = linear.combo)
```
#The 95%-confidence interval for is given by (4.90354, 6.46482) as the the first contrast is zero or not, and the average value of Î¼1 and Î¼2 as 5.68418 and we are rejecting the null hypothesis because the p-value is <2e-16. The 95%-confidence interval for is given by (-0.13024, -0.09026) as the the second contrast is zero or not, and the average value of Î¼1 and Î¼2 as -0.11025 and we are rejecting the null hypothesis because the p-value is <2e-16. The 95%-confidence interval for is given by (-1.39217, 6.33212) as the the first contrast is zero or not, and the average value of Î¼1 and Î¼2 as 2.46997 and we are not rejecting the null hypothesis because the p-value is 0.1373. The 95%-confidence interval for is given by (-0.18435, 0.01688) as the the second contrast is zero or not, and the average value of Î¼1 and Î¼2 as -0.08374 and we are rejecting the null hypothesis because the p-value is 0.0531.  

#2.4.32
#pi/( 1âˆ’pi)=e^ð›½1X1+ð›½2X2+ð›½3X3+ð›½4X1X2+ð›½5X1X3+ð›½6X2X3+ð›½7X1X2X3
#then we could set X2 = E(X2) and X3 = E(X3). 
#1)When X1 = 1, pi/(1âˆ’pi)=e^ð›½1+ð›½2E(X2)+ð›½3E(X3)+ð›½4E(X2)+ð›½5E(X3)+ð›½6E(X2)E(X3)+ð›½7E(X2)E(X3)
#2)When x1 = 0, pi/(1âˆ’pi)=e^ð›½2E(X2)+ð›½3E(X3)+ð›½6E(X2)E(X3)
#Therefore, we could get the odds ratio = e^ð›½1+ð›½4E(X2)+ð›½5E(X3)+ð›½7E(X2)E(X3)
#we can notice that this estimator do not contain any x1