---
title: "HW7_Sabrina Liu"
output: html_document
---

#1(a)
```{r}
crab = read.table("HorseshoeCrabs.txt") 
color = crab[,1]
spine = crab[,2]
width = crab[,3]
satell = crab[,4]
weight = crab[,5]
y = as.numeric(satell > 0) 
color = color-1 
crab.data = data.frame(cbind(color, spine, width, satell, weight, y))
crab.data

model.weight = glm(y~weight, data = crab.data, family = binomial(link = "logit"))
summary(model.weight)
model.weight$coefficients
```
#1(b)
```{r}
w_1 = 1200
w_2 = 2440
w_3 = 5200

#1.2g = 1200g
pi_1 = model.weight$coefficients[1] + model.weight$coefficients[2] * w_1
pi_1
#2.44kg = 2440g
pi_2 = model.weight$coefficients[1] + model.weight$coefficients[2] * w_2
pi_2
#5.20 = 5200g
pi_3 = model.weight$coefficients[1] + model.weight$coefficients[2] * w_3
pi_3
```
#1.20 is the sample minimun, 2.44 is the sample mean, and 5.2 is the sample maximum.

#1(c)
```{r}
p = 0.50
weight_1 = log(p/(1-p)) - model.weight$coefficients[1]/model.weight$coefficients[2]
weight_1
```

#1(d)
```{r}
#(i) increase 1kg
model.weight$coefficients[2]*1000
#(ii) increase 0.1
model.weight$coefficients[2]*100
#(iii) increase 0.58
model.weight$coefficients[2]*580
```

#2.4.5(a)
```{r}
library(car)
library(dplyr)
library(ggplot2)
challenger <- read.table(file = "challenger.csv", header = TRUE, sep = ",", stringsAsFactors = T , dec=",")
model.temp = glm(as.factor(challenger$O.ring) ~ as.factor(challenger$Temp), family = binomial(link = "logit"))
summary(model.temp)
```

#2.4.5(b)
```{r}
model2 = glm(O.ring/Number ~ Temp, data = challenger, family = binomial, weights = Number)
#pi vs. Temp
new_challenger <- data.frame(Temp = seq(from = 31, to = 81, by = 1))
lp.hat <- predict.glm(model2, newdata = new_challenger, type = "link", se.fit = TRUE)
lp.hat.mean <- lp.hat$fit
pi.hat <- exp(lp.hat.mean) / (1 + exp(lp.hat.mean))
plot(new_challenger$Temp, pi.hat, ylim = range(c(0,1)),
     xlab = "Temperature", ylab = "Predicted Prob of single O-ring failure", 
     main = "Predicted Pi vs. Temperature", type = 'l', col = 'black', lwd = 2)
#expected number of failures vs. Temp
plot(new_challenger$Temp, pi.hat * 6, ylim = range(c(0,6)),
     xlab = "Temperature", ylab = "Predicted Number of O-ring failures", 
     main = "Predicted O-ring Failures vs. Temperature", type = 'l', col = 'blue', lwd = 2)
```

#2.4.5(d)
```{r}
  linear.pred<-model.temp$coefficients[1] + model.temp$coefficients[2]*31
  linear.pred
  exp(linear.pred)/(1+exp(linear.pred))
  as.numeric(exp(linear.pred)/(1+exp(linear.pred)))  # Removes label
  plogis(q = linear.pred)  # This uses the inverse of the CDF of a logistic distribution
  
  predict.data<-data.frame(Temp = 31)
  predict(object = model.temp, newdata = predict.data, type = "link")
  predict(object = model.temp, newdata = predict.data, type = "response")
  model.temp$fitted.values[3] 
```

#2.4.5(e)
```{r}
sigmoid = function(x) {1 / (1 + exp(-x))}
#start with the parameter estimates from our model and our Temp data
beta0 = model2$coefficients[1]
beta1 = model2$coefficients[2]
x <- challenger$Temp
pi <- sigmoid(beta0 + beta1*x)
weights <- challenger$Number

sim <- function(){
  #simulate new O.ring failure counts as binomial random variable with n=6 trials and p=pi probability of success
  y <- rbinom(n = length(x), size = 6, prob = pi)
  #fit a new regression model on the simulated O.ring failure counts
  mod.fit <- glm(y/weights ~ x, family = binomial, weights = weights)
  beta0.star = mod.fit$coefficients[1]
  beta1.star = mod.fit$coefficients[2]
  #use new model to compute predicted probability of O.ring failure at Temp = 31 and 72 degrees
  pi_star.31degrees <- sigmoid(beta0.star + beta1.star*31)
  pi_star.72degrees <- sigmoid(beta0.star + beta1.star*72)
  return(c(pi_star.31degrees,pi_star.72degrees))
}
#run simulation 10000 times
n=10000
sim_vals <- replicate(n,sim())
quantile(sim_vals[1,],c(0.05,0.95))
quantile(sim_vals[2,],c(0.05,0.95))
```

#2.4.13(a)
#In this case we use contigency table to interpretate the relationship between first trial and second trial. 

#2.4.13(b)
```{r}
c.table<-array(data = c(251, 48, 34, 5), dim = c(2,2), dimnames = list(First = c("made", "missed"),
             Second = c("made", "missed")))
bird1 <- as.data.frame(as.table(c.table))
trials <- aggregate(formula = Freq ~ First, data = bird1, FUN = sum)
success <- bird1[bird1$Second == "made", ]
bird2 <- data.frame(First = success$First, success = success$Freq , trials = trials$Freq)
bird2

model.first.ungrouped = glm(as.factor(bird2$success) ~ as.factor(bird2$First), data = bird2, family = binomial)
summary(model.first.ungrouped)

```
#2.4.13(c)
```{r}
  OR.hat<-c.table[1,1]*c.table[2,2] / (c.table[2,1]*c.table[1,2])
  round(OR.hat, 2)
  round(1/OR.hat, 2)

  alpha<-0.05
  var.log.or<-1/c.table[1,1] + 1/c.table[1,2] + 1/c.table[2,1] + 1/c.table[2,2]
  OR.CI<-exp(log(OR.hat) + qnorm(p = c(alpha/2, 1-alpha/2)) *
        sqrt(var.log.or))
  round(OR.CI, 2)
  
  
  exp(model.first.ungrouped$coefficients[2])
  exp(-10*model.first.ungrouped$coefficients[2])
```

#2.4.13(e)
#Since one is for logistic regression model and one is for different probabilities.

#2.4.21(a)
```{r}
#logit(π) = β0 + β1x
#logit(π) - β0 = β1x
#(logit(π) - β0) / β1 = x
```

#2.4.21(b)
 











#2.4.22(a)
```{r}
Picloram <- read.table(file = "picloram.csv", header = TRUE, sep = ",")
model.picloram <-glm(formula = kill/total ~ picloram, weight = total, family = 
    binomial(link = logit), data = Picloram)
summary(model.picloram)
```

#2.4.22(b)
```{r}
plot(x = Picloram$picloram, y = Picloram$kill/Picloram$total, xlab = "Picloram", ylab = 
    "Estimated kill rate", col = rep(x = c("black", "blue", "orange"), each = 4), 
    pch = rep(x = 1:3, each = 4))
curve(expr = plogis(q = model.picloram$coefficients[1] + model.picloram$coefficients[2]*x), add 
    = TRUE, col = "red", xlim = c(min(Picloram$picloram), max(Picloram$picloram)))
legend(x = 3, y = 0.4, legend = c("Rep 1", "Rep 2", "Rep 3"), col = c("black", 
    "blue", "orange"), pch = c(1,2,3), bty = "n")
```
#2.4.22(c)
```{r}
plot(x = Picloram$picloram, y = Picloram$kill/Picloram$total, xlab = "Picloram", ylab = 
    "Estimated kill rate", col = rep(x = c("black", "blue", "orange"), each = 4), 
    pch = rep(x = 1:3, each = 4))
curve(expr = plogis(q = model.picloram$coefficients[1] + model.picloram$coefficients[2]*x), add 
    = TRUE, col = "red", xlim = c(min(Picloram$picloram), max(Picloram$picloram)))
legend(x = 3, y = 0.4, legend = c("Rep 1", "Rep 2", "Rep 3"), col = c("black", 
    "blue", "orange"), pch = c(1,2,3), bty = "n")
pi0<-0.9
LD<-(log(pi0/(1-pi0)) - model.picloram$coefficients[1])/model.picloram$coefficients[2]
as.numeric(LD)

segments(x0 = -1, y0 = pi0, x1 = LD, y1 = pi0, lty = "dashed")
segments(x0 = LD, y0 = -1, x1 = LD, y1 = pi0, lty = "dashed")

```

#2.4.22(d)
```{r}
root.func <- function(x, model.picloram.obj, pi0, alpha) { beta.hat <- model.picloram.obj$coefficients
cov.mat <- vcov(model.picloram.obj)
var.den <- cov.mat[1,1] + x^2*cov.mat[2,2] +
2*x*cov.mat[1,2]
abs(beta.hat[1] + beta.hat[2]*x - log(pi0/(1-pi0))) /
sqrt(var.den) - qnorm(1-alpha/2) }
lower <- uniroot(f = root.func, interval = c(min(Picloram$picloram), LD), model.picloram.obj = model.picloram, pi0 = 0.9, alpha = 0.05)
lower # lower$root contains the lower bound
upper <- uniroot(f = root.func, interval = c(LD, max(Picloram$picloram)), model.picloram.obj = model.picloram, pi0 = 0.9, alpha = 0.05)
upper # upper$root contains the upper bound
```

#2.4.22(e)
#According to previous question, we would prefer 2.45 dosage in this case since we are 95% confident that this is a safe choice. 

#2.4.22(f)
#1) There are n identical trials. 2) There are two possible outcomes for each trial. 3) The trials are independent of each other. 4) The probability of success remains constant for each trial. 5) The random variable of interest W is the number of successes.